Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-22 paper/paper.tex
Update paper.tex
diff

\begin{abstract}
  Automated Machine Learning or AutoML has emerged as a popular field of research. We performed a literature review of existing AutoML papers and conducted a survey on six popluar AutoML frameworks. Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated. We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant so unnecessary time is not spent training these models. SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" model that runs every model on every dataset, but in a fraction of the time.
\end{abstract}

>>>>

\begin{abstract}
  Automated Machine Learning or AutoML has emerged as a popular field of research. We performed a literature review of existing AutoML papers and conducted a in depth survey on six popluar AutoML frameworks. Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated. We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant so unnecessary time is not spent training these models. SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force model that runs every model on every dataset, but in a fraction of the time.
\end{abstract}
